### 2014-12-19 paper_10_intro.tex
capitalize titles and rearrange  sections
adding some new references
fixed Schedule chapter problem starting to work on SEMAT section

% see this for  guidance https://www.cs.purdue.edu/homes/dec/essay.dissertation.html
\section{Introduction}

@@

\subsection{Background}

@@

\subsection{Previous Software Engineering Scoring Attempts}

@@

>>>>

% see this for  guidance https://www.cs.purdue.edu/homes/dec/essay.dissertation.html
\section{INTRODUCTION}

@@

\subsection{BACKGROUND}

@@

\subsection{PREVIOUS SOFTWARE SCORING ATTEMPTS }

@@

Quality is tested in \cite{Miguel2014}

See also \cite{Buse2010}.

\subsubsection{SEMAT}

SEMAT is being dubbed as the ``new software engineering'' \cite{Jacobson2014}.
Three parts to the kernel:
\begin{itemize}
\item Measurement
\item Categorization
\item Competencies
\end{itemize}

The seven dimensions:
\begin{itemize}
\item Opportunity
\item Stakeholders
\item Requirements
\item Software Systems
\item Work
\item Team
\item Way of Working
\end{itemize}

\subsection{ORGANIZATION OF THE WORK}

The remainder of this dissertation is divided into 5 chapters.  The next chapter provides
an overview of software, software development lifecycles, software engineering, and software
development organizations.  Chapter 3 introduces what is meant by the term data-driven
software engineering. Chapter 4 then provides an explanation of the Master Performance 
Indicator (MPI).  It will present the essential elements for calculating the MPI, as well
as the formulas, frameworks, and data necessary to produce the MPI. Chapter 5 provides
a technological framework for generating and storing the current and historical MPI values.
Chapter 6 demostrates how MPI can be implemented in a software development portion of 
a large financial institution.  Chapter 7 concludes the dissertation with a summary
of the results and some possible future directions for further enhancements.

### 2014-12-19 paper_40_mpi.tex
fixed Schedule chapter problem starting to work on SEMAT section

\subsection{SCHEDULE}
Delivery of software in a timely manner is important.  Therefore, it is critical to know whether software was released early, late, or on-time.  
The best possible score should be achieved
            when meeting the estimated date exactly.  The maximum score
            should come from the best estimate.  Then given historical
            release data, it is easy to determine an 
            average $\Delta$ between the actual and the estimated.  
            Finishing a project within that $\Delta$ should result 
            in a positive score.  Outside the $\Delta$ results in
            negative scores.  For example, a project releasing
            one day early or one day late would receive the same score
            because in both cases the estimate was missed by one day.

\section{Schedule Adherence}
    \subsection{Overview}
        Delivery of software in a timely manner is an essential part of being a 
        successful SDO.  Being able to meet scheduled deadlines is a sign of accurate
        estimation and planning.  Drastically missing deadlines is a sign of an SDO
        with a process that needs refinement.  Studies have shown that 
        software projects exceed the estimates by an average of
        30\% \cite{Jorgensen2014}.  Thus it is important to score SDOs on accurate
        schedule adherence. Without tracking and measuring schedule adherence, it will
        not improve.

@@

    \newpage
    \subsection{Formula}

@@

    \subsection{Example Calculation}
    \subsection{Data and Calculations}
    \subsubsection{Obtain the Data}
    \subsubsection{Run the Calculations}
    \subsection{Past Performance}
    \subsection{Process for the Future}

>>>>

\subsection{SCHEDULE}

    \subsubsection{Overview}
        Delivery of software in a timely manner is an essential part of being a 
        successful SDO.  Being able to meet scheduled deadlines is a sign of accurate
        estimation and planning.  Drastically missing deadlines is a sign of an SDO
        with a process that needs refinement.  Studies have shown that 
        software projects exceed the estimates by an average of
        30\% \cite{Jorgensen2014}.  Thus it is important to score SDOs on accurate
        schedule adherence. Without tracking and measuring schedule adherence, it will
        not improve.

@@

    \subsubsection{Formula}

@@

    \subsubsection{Example Calculation}
    \subsubsection{Data and Calculations}
    \subsubsection{Past Performance}
    \subsubsection{Process for the Future}

    \subsubsection{ALTERNATE APPROACH}
    The best possible score should be achieved
            when meeting the estimated date exactly.  The maximum score
            should come from the best estimate.  Then given historical
            release data, it is easy to determine an 
            average $\Delta$ between the actual and the estimated.  
            Finishing a project within that $\Delta$ should result 
            in a positive score.  Outside the $\Delta$ results in
            negative scores.  For example, a project releasing
            one day early or one day late would receive the same score
            because in both cases the estimate was missed by one day.
